---
title: "IVF Audit"
author: "M.Mohamed,F.Binti Zahri"
output:
  pdf_document: 
    number_sections: no
    toc: yes
    toc_depth: 4
  html_notebook:
    fig_caption: yes
    toc: yes
  word_document:
    toc: yes
---

```{r load-packages,include=F}
source("explore.r")
library(tidyverse)
library(ggnewscale)
library(magrittr)
library(here)
library(RColorBrewer)
library(forcats)
library(extrafont)
library(tableone)
loadfonts()
setwd(here::here())

source('../RFunctions/colorize.R')
```
```{r include=F}
knitr::opts_chunk$set(echo=F, error=F, fig.align='center', fig.height=4.5, fig.width=8, message=FALSE, warning=FALSE, dev='png', dpi=400)
```

\newpage


## Are We Compliant with NICE Clinical Guidance No. 174?

### Table 1.1 Overall Compliance Shown Over Weekdays vs Weekends
#### It seems we have slightly worse performance over the weekend- Not statistically tested
```{r}
iv2 <- iv
colnames(iv2) <-  savenames
iv2[,17:19] %<>% lapply(.,factor,levels=c('Yes','No','Not Required'),ordered = T)
a<- print(CreateTableOne(data = iv2[-c(1,2)],vars = colnames(iv2[-c(1,2,5)]),strata = colnames(iv2)[5],),printToggle = F,test = F,showAllLevels = T)

a %<>% kableone(justify="left",)

a


```

### Plot 1  IVF Requirment Documentation
```{r}
p1 <- ggplot(iv,aes(WD))+
  geom_bar( aes(fill=IVDOC.notes),position = 'dodge')+
  scale_fill_viridis_d(option = "cividis")+scale_y_continuous(n.breaks = 8)
```


```{r}
p1+labs(x="Day",y="Number of Patients",fill="IVF Requirment \ndocumented in notes")+ theme(title = element_text(face="bold"))


```

### Plot 2 Compliance to Appropriate Fluids Prescription
```{r}
p2 <- melt(iv,measure.vars =c('AppMain','AppReplace','AppResus'),value.name = "Indication") %>%
  filter(Indication!="Not Required") %>%
  ggplot(aes(variable,fill=fct_infreq(Indication)))+
  geom_bar(position = 'dodge')+
  scale_x_discrete(labels=c("Appropriate Maintenance","Appropriate Replacement"))+
  scale_fill_viridis_d(option = "cividis")+
  scale_y_continuous(n.breaks = 8)


p2+ 
  labs(  x="Indication",
         y="Number of Patient",
         fill=" Appropriate Fluid \nfor Indication Prescribed?")+
  theme(title = element_text(face="bold"))
```

### Plot 3 Compliance to Daily Reviews and Proper Documentation
```{r}
prop1 <- melt(iv,measure.vars = names(iv[c(8,10:12)]),variable.name = "measuredindicator",value.name ="achieved" ) %>%
  group_by(measuredindicator,achieved) %>%
  summarise(count=sum((as.numeric(as.factor(achieved)))),prop=round(count/32,2)) %>% filter(achieved=="Yes")

p3 <- melt(iv,measure.vars = names(iv[c(8,10:12)]),
           variable.name = "measuredindicator",
           value.name ="achieved" )%>% 
  ggplot(aes(x=measuredindicator,fill=achieved))+geom_bar(position = "fill")+
  scale_fill_viridis_d(option="cividis")+
  geom_label(data=prop1,aes(x=measuredindicator,y=prop),label=prop1$prop)+
  scale_x_discrete(labels=str_wrap(c("Weighed every 7 days","U&E's every 24 hours","Fluid Indication Noted In Plan","24 hour fluids prescribed or fluid plan documented"),15))

p3 +
  theme(title = element_text(face="bold"))+
  labs(x="Measured Indicator",
       y="Proportion of patients",
       caption="Fluid Indication is one of 3 as per NICE guidance. Resus. Replace. Maintain",
       fill="Has it been\nachieved?")

```

### Plot 4.1 Compliance to IVF Specifications
```{r}
prop2 <- melt(iv,measure.vars = names(iv[c(14:16)]),variable.name = "measuredindicator",value.name ="achieved" ) %>%
  group_by(measuredindicator,achieved) %>%
  summarise(count=sum((as.numeric(as.factor(achieved)))),prop=round(count/32,2)) %>% filter(achieved=="Yes")

p4 <- 
  melt(iv,measure.vars = names(iv[c(14:16)]),variable.name = "measuredindicator",value.name ="achieved" ) %>%
  ggplot(aes(x=measuredindicator,fill=achieved))+geom_bar(position = "fill")+
  scale_fill_viridis_d(option="cividis")+
  geom_label(data=prop2,aes(x=measuredindicator,y=prop),label=prop2$prop)+
  scale_x_discrete(labels=str_wrap(c("IVF Volume Noted","IVF Rate Noted","Maintaince dose IV K+ Prescribed"),15))
p4 +
  labs(x="Measured Indicator",
       y="Proportion of patients",
       caption="Daily Fluid Requirment: 25-30ml/Kg (20-25ml/Kg if frail or allowing for HF)
             \nDaily Na+ & K+ Requirments : 1 mmol/Kg",
       fill="Has it been\nachieved?")+
  theme(title = element_text(face="bold"))
```

### Plot 4.2
```{r}
p5<- 
  ggplot(iv,aes(fct_infreq(Composition)))+
  geom_bar(fill="navy",alpha=0.7)+ 
  scale_x_discrete(labels=lapply(as.character(levels(fct_infreq(iv$Composition))),str_wrap,15))            

p5 +
  labs(x="Composition",
       fill="Appropriate Fluid for Indication Prescribed")+
  theme(title = element_text(face="bold"))
```
```{r}
p2 <- melt(iv,measure.vars =c('AppMain','AppReplace','AppResus'),value.name = "Indication") %>%
  filter(Indication!="Not Required") %>%
  ggplot(aes(variable,fill=fct_infreq(Indication)))+
  geom_bar(position = 'dodge')+
  scale_x_discrete(labels=c("Appropriate Maintenance","Appropriate Replacement"))+
  scale_fill_viridis_d(option = "cividis")+
  scale_y_continuous(n.breaks = 8)


p2+ 
  labs(  x="Indication",
         y="Number of Patient",
         fill=" Appropriate Fluid \nfor Indication Prescribed?")+
  theme(title = element_text(face="bold"))



iv %>% filter(AppMain!="Not Required",)%>%  ggplot( aes(fct_infreq(Composition),fill=AppMain))+
  geom_bar()+
  scale_fill_viridis_d(option = "cividis")+
  labs(title="Was Appropriate Maintenance Fluid Type Prescribed?",x="Fluid Composittion",fill="Appropriate Maintenance \nFluid Prescribed")

iv %>% filter(AppReplace!="Not Required",)%>%  ggplot( aes(fct_infreq(Composition),fill=AppReplace))+
  geom_bar()+
  scale_fill_viridis_d(option = "cividis")+
  labs(title="Was Appropriate Replacement Fluid Type Prescribed?",x="Fluid Composittion",fill="Appropriate Maintenance \nFluid Prescribed")
```

Over 20 instances of IVF prescription recorded on overnight shift on nerver centre for period of assesment.



### Fluid Status Assement
```{r}
p <- iv %>% ggplot(aes(x=FluidStatusDOC,fill=FluidStatusDOC))+
  geom_bar() +
  scale_fill_viridis_d(option = "cividis")+
  labs(x=NULL,fill="Fluid Status") + 
  theme(axis.text.x =element_blank(), 
    legend.position = "bottom", legend.direction = "horizontal")
ggsave(plot=p,'fluidstat',device = 'png',dpi = 410)
p

```
